### 2015-11-04 CVPR16/Source/experiments.tex
Changed the color of correct points to blue instead of red.

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Associations & Error in association\\
    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results of the association experiment. The left column
  shows the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. Right column shows the
probabilistic error in association: low errors are in red while high errors are in blue.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0-1 error.} 
\end{table*}

@@

We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
We use the following energies in our graphical model.

@@

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
    $\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
    % \EnergyBBox+\EnergyDyn+\EnergyCol $
    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
  \label{tab:localizationExperiment}
\end{table}

>>>>

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Associations & Error in association\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results of the association experiment. The left column
  shows the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. Right column shows the
probabilistic error in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0-1 error.} 
\end{table*}

@@

We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Next, we explain the important energies used in our graphical model.

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution.

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
    %$\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
    % \EnergyBBox+\EnergyDyn+\EnergyCol $
    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
  \label{tab:localizationExperiment}
\end{table}
